---
title: "Week 14 IP anomaly Detection"
author: "Njoki Mbugua"
date: "7/17/2021"
output: html_document
---
```{r}
library(knitr)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#  Defining the Question
## a) Specifying the Question
The objective of this project fraud detection by checking whether there are any anomalies in the given sales dataset that could point out potential fraud activity.
## b) Defining the Metric for Success
Exhaustively performing anomaly detection without any errors.

## c) Understanding the context
Working as a consultant Data analyst at Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax).This project endeavors to  explore a recent marketing dataset and check whether there are any anomalies in the given sales dataset that could point out potential fraud activity.

## d) Recording the experimental design
Importing and reading the data
Data Cleaning
Anomalies detection
Conclusions and recommendations

## e) Data Relevance
The data was provided by the company (http://bit.ly/CarreFourSalesDataset). 

# Loading and previewing the data
```{r}
# url= http://bit.ly/CarreFourSalesDataset
sales = read.csv('http://bit.ly/CarreFourSalesDataset') 
```


```{r}
head(sales)
```
# Loading the libraries
```{r}
library(tidyverse)
library(tibbletime)
library(anomalize)
library(lubridate)
library(dbplyr)

```

```{r}
# Checking the structure of the dataset to view the datatype of the date column
str(sales)
```

```{r}
# Change date from character to Date format

sales$Date <- mdy(sales$Date)
#sales$Date <- as.Date(sales$Date, format ="%m/%d/%Y")
sales$Date <- sort(sales$Date, decreasing = FALSE)

```


```{r}
# Converting dataframe to tibble format
df <- as_tbl_time(sales, index = Date)
df1 <- df %>%
    as_period("daily")
```

```{r}
# Previewing the tibble
head(df1)

```

```{r}
# Checking the class of the dataset
class(df1)

```
```{r}
# Using the anomalize package to detect anomalies
df1 %>%
  time_decompose(Sales, method = "stl") %>%
  anomalize(remainder, method = "iqr") %>%
  time_recompose() %>%

# Anomaly Visualization
  plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.25)
  
```
The data provided doesn't contain any anomalies.


